A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-01-17 paper/submission/ZW10157-response-1.tex
add an other suggestions for an answer
more edits to response 1

With the best regards  \\[3mm]

@@

{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}

@@

{\bf Our response:} {\color{blue} XXXXX.}

@@

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
	Especially the following:

@@

	We thank the reviewer for the list of references. 
	References described or referenced by A. Hofler in the above were excluded from 
	the bibliography. 
}

1) References for 4 PISA-based optimization systems:

{\color{blue}{Included in updated bib:}}

{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}

@@

@@

2) Optimization systems using NSGA-II (a few example references):

@@

M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062

3) Survey with various references showing GA/EA usage in Accelerator
Physics: A. Hofler. “Genetic Algorithms and Their Applications in
Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1

@@

{\bf Our response:} {\color{blue} XXXXX.}

Third, several of the features of this system are available is
existing systems but are not acknowledged:

@@

{\bf Our response:} {\color{blue} XXXXX.}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design. For example, in the main text, it is
reasonable to say that the optimization system provides a flexible and
extensible meta-language for setting up optimization problems (covered
in detail in Section III subsection E) and then direct the reader to
an Appendix or the Supplemental Material for the details provided in
Section III subsection E. Bear in mind, though, that several of the
PISA-based systems mentioned above, also, provide expression
capabilities and should be referenced. The one presented here is more
flexible and has the advantage of being easily extended. Both are
distinguishing features. The authors need to emphasize what
differentiates their system from 13+ years of development in the area
of GA/EA-based optimization in accelerator design and then demonstrate
that the results produced are exemplary or could not have been
produced otherwise. Or they should focus on how their system advances
the application of the target AWA machine (the Gulliford references
use this approach).

@@

{\bf Our response: } {\color{blue} XXX}

>>>>

With the best regards,  \\[3mm]

@@

{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.
A link to the repository was provided, interested parties can see the code examples there.}

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:
	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT~\cite{gpt} and ELEGANT~\cite{borl:00}, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.
}

@@

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
	Especially the following: }

@@

{\bf Our response:} {\color{blue} 	We thank the reviewer for the list of references. 
	Next, one by one in the list, we indicate which references were included in the updated bibliography: 
}

{\color{blue}{Included in updated bibliography (in addition to two references above):}}

M. Borland. ELEGANT: A flexible SDDS-compliant code for accelerator simulation, 2000-2018.
{\color{blue}{(slightly updated this reference)}}

{\color{blue}{Exluded from updated bibliography, because  they are in A. Hofler 13':}}

@@

{\color{blue}{Excluded because of similarity to other references or scope of paper:}}

@@

@@

A. Hofler. “Genetic Algorithms and Their Applications in
Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1

\vspace{5em}

@@

{\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognized. We replace them with the following:

Despite the success of on-line models in some facilities[ref here], and various model dependent and model independent tuning and optimization techniques, in research facilities like the AWA, empirical tuning by operators is still one of the common methods used. Due to the non-linear problem mainly from space charge, simple and fast models are applicable only in a very restricted manner. When it comes to multi-objective optimization, the situation is even more complicated.
}

Third, several of the features of this system are available in
existing systems but are not acknowledged:

@@

{\bf Our response:} {\color{blue} We hope we have addressed these comments with the additional references included above, correction of lines 17-19, 
	and the additions provided in response to Referee A's remarks.}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design.

{\bf Our response:} {\color{blue} 
	Respectfully, we point out Referee A's comments that 
	"Computing and algorithms" is listed under PRAB's scope. 
	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
	we had hoped the AWA optimization problem would 
	provide a meaningful and tangible use case for the framework.
	It seems we did not present that part of the paper strongly enough. 
	We hope some of the additions above have helped in this area.
	However, would also like to keep some computational details for those who 
	may be interested in code development specifically for accelerator optimization.
}

For example, in the main text, it is
reasonable to say that the optimization system provides a flexible and
extensible meta-language for setting up optimization problems (covered
in detail in Section III subsection E) and then direct the reader to
an Appendix or the Supplemental Material for the details provided in
Section III subsection E. Bear in mind, though, that several of the
PISA-based systems mentioned above, also, provide expression
capabilities and should be referenced.

{\bf Our response:}{\color{blue} 	
	We have removed all opal related code, and shortened these sections.
	Additional references now point out ELEGANT and GPT have built in genetic optimization.
}

The one presented here is more
flexible and has the advantage of being easily extended. Both are
distinguishing features. The authors need to emphasize what
differentiates their system from 13+ years of development in the area
of GA/EA-based optimization in accelerator design and then demonstrate
that the results produced are exemplary or could not have been
produced otherwise. Or they should focus on how their system advances
the application of the target AWA machine (the Gulliford references
use this approach).

{\bf Our response:}{\color{blue} 	
	We hope the additions above are addressing these issues. }

@@

{\bf Our response: } {\color{red} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms. Something that you can not find in most of the 
existing codes.}

### 2019-01-17 paper/submission/prab.tex
more edits to response 1

\begin{figure}%[h!]
%\begin{center}%\normalsize
	\scalebox{0.8}{
	\pgfdeclarelayer{background}
	\pgfsetlayers{background,main}
	\begin{tikzpicture}[text=black]%[scale=0.05]%, transform shape]
	\input{figures/opt-framework_code.tex}
	\end{tikzpicture}
}
%\end{center}
\caption{Multi-objective framework: the pilot (master) solves the
	optimization problem specified in the input file by coordinating optimizer
	algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{figure}

@@

Often, conflicting objectives are encountered, and this complicates the concept of
  optimality.

  \iffalse
To illustrate this, let us consider the problem of buying a car.
Naturally, we try to bargain the lowest price for the best performance,
  e.g.\ maximal horsepower or minimal fuel consumption.
This can be formulated as MOOP (\ref{eq:car-moop}).
%
\begin{equation}
  \begin{array}{cl}
  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
  \end{array}
  \label{eq:car-moop}
\end{equation}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}[scale=1.3, transform shape]
      \input{figures/car-trade-off}
    \end{tikzpicture}
  \end{center}
  \caption{Two competing objectives can not be optimal at the same time.
    Red dots represent Pareto optimal points, while the green square $x_4$ is
    dominated (exhibits a worse price per performance ratio than e.g. $x_2^*$)
    by all points on the blue curve (Pareto front).
  }
  \label{fig:tradeoff}
\end{figure}

In general, it is not possible to get the maximal performance for the lowest
  price and a trade off decision between performance and price has to be
  reached (see Fig.~\ref{fig:tradeoff}). 
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
  \fi
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.

>>>>

\begin{figure}%[h!]
	\center
\includegraphics[width=0.5\textwidth]{figures/opt-framework_code}
\caption{Multi-objective framework: the pilot (master) solves the
	optimization problem specified in the input file by coordinating optimizer
	algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{figure}

@@

Often, conflicting objectives are encountered, and this complicates the concept of
  optimality.
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.
